% \chapter*{Images Cited}
\newpage 
\addcontentsline{toc}{chapter}{Images Cited}
\setheader{Images Cited}
\begin{imagescited} 
\begin{flushleft}
\linespread{1.5}

Cover: \\
\bibent
Study in Numbers. Photograph. n.d. “BSc Marine Technology”. \textit{Delft University of Technology}. TU Delft, 2016. Web. 14 May 2016. \\ \vspace{3mm}

Figure \ref{fig:Bohbot}: \\
\bibent
\textit{Empty Parisian Theatre}. Photograph. n.d. “10 Symmetrical Parisian Theatres that Will Make You Dizzy”. \textit{HuffPost Arts \& Culture}. HuffingtonPost.com, Inc., 2016. Web. 14 May 2016. \\ \vspace{3mm}

Figure \ref{fig:Portrait of Callie Hernandez}: \\
\bibent
\textit{Portrait of Callie Hernandez}. Photograph. n.d. “Callie Hernandez”. \textit{IMDb}. IMDb.com, Inc., 1990-2016. Web. 14 May 2016. \\ \vspace{3mm}

Figure \ref{fig:Typewriter}: \\
\bibent
“Typewriter.” Photograph. Miller, John. “Brand Journalism > Content Marketing.” \textit{Business 2 Community}. Business 2 Community, 11 May 2014. Web. 14 May 2016. \\ \vspace{3mm}

Figure \ref{fig:Building a Computer}: \\
\bibent
WIX. “Building a Computer.” WIX Clipart. Web. 14 May 2016. \\ \vspace{3mm}

Figure \ref{fig:Tall Buildings}: \\
\bibent
WIX. “Tall Buildings.” WIX Clipart. Web. 14 May 2016. \\ \vspace{3mm}

Figure \ref{fig:Film Making}: \\
\bibent
\textit{Filmmaking}. Photograph. n.d. “Filmmaking Tips”. \textit{Lesson Bucket}. Brett Lamb, n.d. Web. 14 May 2016. \\ \vspace{3mm}

Figure \ref{fig:Doctor Desk}: \\
\bibent
WIX. “Doctor Desk.” WIX Clipart. Web. 14 May 2016. \\ \vspace{3mm}

Figure \ref{fig:Curators looking at art}: \\
\bibent
WIX. “Curators looking at art.” WIX Clipart. Web. 14 May 2016. \\ \vspace{3mm}

Figure \ref{fig:Business report}: \\
\bibent
WIX. “Business report.” WIX Clipart. Web. 14 May 2016. \\ \vspace{3mm}

\end{flushleft}
\end{imagescited} 