% \chapter*{Works Cited}
\newpage 
\newpage 
\addcontentsline{toc}{chapter}{Works Cited}
\setheader{Works Cited}
\begin{workscited}
\begin{flushleft}
\linespread{1.5}

\bibent
Abraham, Nikhil. “Pros and Cons of the JD/MBA.” \textit{JD/MBA Blog Post}. The University of Chicago, 2009. Web. 23 Apr. 2016.

\bibent
“Art History Basics.” \textit{Khanacademy.org}. Khan Academy, 2015. Web. May 2016.

\bibent
“Art History, Criticism, and Conservation College Degree Programs.” \textit{Art History, Criticism, and Conservation College Degree Programs - The College Board}. The College Board, 2016. Web. 1 May 2016.

\bibent
“Art History (in Dutch) - University of Amsterdam.” \textit{Art History - University of Amsterdam}. Faculty of Humanities of University of Amsterdam, 2016. Web. 1 May 2016.

\bibent
“BA History of Art.” \textit{The Courtauld Institute of Art}. The Courtauld Institute of Art, 2015. Web. 1 May 2016.

\bibent
“Bachelor of Arts (BA): Film and Video Production Degree Overview.” \textit{Study.com}. Study.com, 2016. Web. 29 Apr. 2016. 

\bibent
“Best Undergraduate Business Schools For 2016.” \textit{College Choice}. College Choice, 2016. Web. 29 Apr. 2016.

\bibent
“Best Value Business Schools.” \textit{College ROI Report}. Payscale, 2016. Web. 29 Apr. 2016.

\bibent
“Best Value Colleges Engineering Majors.” \textit{PayScale}. PayScale, 2016. Web. 4 May 2016.

\bibent
“Business Majors: The Basics.” \textit{BigFuture}. College Board, 2016. Web. 28 Apr. 2016.

\bibent
“Business Psychologist: Career Info, Job Duties, and Requirements.” \textit{Study.com}. Study.com, 2016. Web. 19 Apr. 2016. 

\bibent
“Careers In Management.” \textit{Texas A\&M University Career Center: College Station}, 2016. Print.

\bibent
Carter, Craig. “Wharton JD/MBA Student Interview with Craig Carter.” Interview by Accepted. \textit{Blog.accepted.com}. Accepted, 28 Mar. 2014. Web. 11 Apr. 2016.

\bibent
“CollegeBoard.com.” \textit{College and Career Planning from MyRoad.com}. The College Board, 2016. Web. 1 May 2016.

\bibent
“College Profile: Michigan State University.” \textit{Collegedata}. 1st Financial Bank, 2015. Web. 19 Apr. 2016. 

\bibent
“College ROI Report: Best Value Colleges for Art Careers.” \textit{PayScale}. PayScale, 2016. Web. 30 Apr. 2016.

\bibent
“Compare Law Schools with JD / MBA Degrees.” \textit{Best Law Schools with JD / MBA Degrees}. StartClass, 2016. Web. 16 Apr. 2016.

\bibent
Cox, Justin. “Is Journalism Grad School Worth It?” \textit{Huffpost College}. TheHuffingtonPost.com, 25 May 2011. Web. 20 Apr. 2016.

\bibent
Crenwelge, Dale. Personal Interview. 20 Apr. 2016.

\bibent
Crenwelge, Drew. Email Interview. 25 Apr. 2016.

\bibent
“Curator.” \textit{The Princeton Review}. TPR Education IP Holdings, 2016. Web. 1 May 2016.

\bibent
“Current Research Projects.” \textit{Faculty of Engineering}. The University of Auckland, n.d. Web. 4 May 2016.

\bibent
“Degree Plans and Requirements.” \textit{Cockrell School of Engineering}. University of Texas at Austin, n.d. Web. 5 May 2016.

\bibent
“Dual Degree: MA in Arts Administration \& Policy \& MA in Modern and Contemporary Art History.” \textit{SAIC}. School of the Art Institute of Chicago, 2016. Web. 1 May 2016.

\bibent
“Electrical and Computer Engineering.” \textit{Cockrell School of Engineering}. University of Texas at Austin, n.d. Web. 5 May 2016.

\bibent
“Engineering Your Graduate School Experience.” \textit{Early Career Engineers, Conferences and Careers}. The American Society of Mechanical Engineers, n.d. Web. 5 May 2016.

\bibent
Esquivel, Gabriel. “Art History Major.” Personal interview. Apr. 2016.

\bibent
Fescoe, Kristen. “Ranking Top 20 Best Graduate Programs in Industrial/Organizational Psychology and Behavioral Neuroscience in 2014.” \textit{Online-psychologydegrees.org}. Online Psychology Degrees, Aug. 2014. Web. 19 Apr. 2016.

\bibent
Freeland, Steven. “I Want Your Job: Interview With Steven Freeland, Professor of International Law, and Visiting Professional at the International Criminal Court.” \textit{Survive Law}. Survive Law, 2012. Web. 15 Apr. 2016. 

\bibent
Geisler, Jill. “Out of Balance: Poynter Survey Reveals Journalists’ Pressure Points.” \textit{Poynter}. The Poynter Institute, 21 Feb. 2005. Web. 11 Apr. 2016.

\bibent
Goudreau, Jenna. “Top 10 Tips for Aspiring Young Journalists.” \textit{ForbesWoman}. Forbes, 9 Nov. 2012. Web. 9 Apr. 2016.

\bibent
Haynie, Devon. “Choose Between a Master’s, Ph.D. in Engineering.” \textit{US News \& World Report}. US News, 16 Mar. 2015. Web. 4 May 2016. 

\bibent
“History of Art - MA (Hons).” \textit{Edinburgh College of Art}. University of Edinburgh, 2015. Web. May 2016.

\bibent
“How Many Hours A Week Does A Lawyer Work?”. \textit{Career Igniter}. Career Igniter, n.d. Web. 19 Apr. 2016. 

\bibent
“How Much Do Associates Work.” \textit{NALP Bulletin}. National Association for Law Placement, n.d. Web. 19 Apr. 2016. 

\bibent 
“Industrial-Organizational Psychologists: Overall Kind of Work.” \textit{Myfuture.com}. Department of Defense, 12 Dec. 2015. Web. 28 Apr. 2016. 

\bibent
“International Law Majors: Salary and Career Facts.” \textit{Learn}.org. Learn.org, n.d. Web. 18 Apr. 2016. 

\bibent
“International Studies: Careers.” \textit{University of North Carolina Wilmington}. UNC Wilmington, n.d. 18 Apr. 2016. 

\bibent
“Journalism Residency at Medill.” \textit{Medill School of Journalism, Media, Integrated Marketing Communications}. Northwestern University, 2015. Web. 14 Apr. 2016. 

\bibent
“Journalist Job Description.” \textit{JournalismDegree.com}. JournalismDegree.com, 2016. Web. 25 Apr. 2016.

\bibent
“Journalist Salary (United States).” \textit{PayScale}. PayScale Inc., 2016. Web. 9 Apr. 2016.

\bibent
Kelle, Jack. “The 25 Most Lucrative Careers in Psychology.” \textit{BestPsychologyDegrees.com}. WordPress, 2016. Web. 19 Apr. 2016. 

\bibent
Lone Star College System. “Energy \& Manufacturing.” \textit{Lone Star College}. Lone Star College System, 2016. Web. 17 May 2016.

\bibent
“Major and Career Search.” \textit{Bigfuture}. The College Board, 2016. Web. 6 Apr. 2016. 

\bibent
“Major: Art History, Criticism, and Conservation.” \textit{Bigfuture}. The College Board, 2016. Web. 1 May 2016.

\bibent
“Management Majors Guide.” \textit{WorldWideLearn}. Quinstreet Inc., 2016. Web. 29 Apr. 2016.

\bibent
“Mechanical Engineering.” \textit{Cockrell School of Engineering}. University of Texas at Austin, n.d. Web. 5 May 2016.

\bibent
Miketinac, Chuck. Personal interview. 18 Apr. 2016. 

\bibent
\textit{College Data}. 1st Financial Bank, 2016. Web. 29 Apr. 2016. 

\bibent
\textit{NYU Department of Art History}. New York University, n.d. Web. 1 May 2016.

\bibent
“Occupational Employment and Wages: 19-3032 Industrial-Organizational Psychology.” \textit{bls.gov}. U.S. Bureau of Labor Statistics, 30 Mar. 2016. Web. 19 Apr. 2016. 

\bibent
“Occupational Outlook Handbook.” \textit{Bureau of Labor Statistics}. United States Department of 
Labor. 17 Dec. 2015. Web. 7 Apr. 2016.

\bibent
“Occupational Outlook Handbook, 2016-2017 Edition”, Actors. \textit{Bureau of Labor Statistics}. U.S. Department of Labor, 17 Dec. 2015. Web. 30 Apr. 2016. 

\bibent
O'Connor, Shawn P. “5 Benefits of a Dual JD/MBA.” \textit{US News}. U.S.News \& World Report, 9 Oct. 2012. Web. 17 Apr. 2016.

\bibent
O’Neil, Brian. “7 Reasons Why An Actor Gets an MFA.” \textit{Backstage}. Backstage, 15 Nov. 2013. Web. 30 Apr. 2016. 

\bibent
“Organizational Leadership Graduate Programs \& Organizational Leadership Graduate Schools. \textit{gradschools.com}. EducationDynamics, 2016. Web. 19 Apr. 2016. 

\bibent
“Organizational Psychology Degrees: What You’ll Study.” \textit{Allpsychologyschools.com}. All Stars Directory, 2016. Web. 19 Apr. 2016.

\bibent
Orsak, Sarah. Personal Interview. 21 Apr. 2016.

\bibent
Parr, Alissa (Ph.D). “5 Things You Didn’t Know About Industrial/Organizational Psychology.” \textit{SelectInternational.com}. Select International, Inc., 2016. Web. 19 Apr. 2016.

\bibent
“PhD IO Industrial Organizational Psychology Doctorate Degrees.” \textit{gradschools.com}. EducationDynamics, 2016. Web. 19 Apr. 2016.

\bibent
“Postgraduate Study in History of Art.” \textit{Bristol University History Department of History of Art}. Bristol University, 2016. Web. 1 May 2016.

\bibent
“Producer or Director.” \textit{Career Profile}. Truity Psychometrics, 2012-2016. Web. 28 Apr. 2016.

\bibent
Ruthsatz, Ria. “No. 126: Ria Ruthsatz, Film Producer.” Interview by Susie Schnall. \textit{The Balance Project}. Susie Schnall, 11 Dec. 2015. Web. 29 Apr. 2016.

\bibent
Sayej, Nadia. “15 Curators to Watch in 2015.” \textit{ArtSlant}. Feb. 2015. Web. May 2016.

\bibent
Smith-Barrow, Delece. “International Law Programs Prepare Students for a Global Career.” \textit{USNews}. U.S. News \& World Report, 14 May 2014. Web. 21 Apr. 2016. 

\bibent
“Sociology Graduate Programs and Sociology Grad Schools.” \textit{gradschools.com}. EducationDynamics, 2016. Web. 19 Apr. 2016. 

\bibent
“Sr. Editor Salary (United States).” \textit{PayScale}. PayScale Inc., 2016. Web. 9 Apr. 2016.

\bibent
“Statistics Graduate Programs \& Data Analytics Graduate Programs.” \textit{gradschools.com}. EducationDynamics, 2016. Web. 19 Apr. 2016. 

\bibent
“The Best Business Schools.” \textit{Forbes}. Forbes Media, 2016. Web 27 Apr. 2016.

\bibent
“Top Schools for Industrial and Organizational Psychology.” \textit{Study.com}. Study.com, 2016. Web. 19 Apr. 2016. 

\bibent
“Top 50 Best Value MBA Programs.” \textit{Value Colleges}. Value Colleges, 2016. Web. 29 Apr. 2016.

\bibent
“TV or Film Producer Job Information.” \textit{TV or Film Producer Job Information}. National Career Services, n.d. Web. 29 Apr. 2016

\bibent
“University of Amsterdam.” \textit{Top Universities}. Quacquarelli Symonds Limited, 2015. Web. 1 May 2016.

\bibent
Wells, Dallin. “What Is the Film Director Lifestyle like for the Spouse?” \textit{Review}. Weblog post. No Film School. Nonetwoek, 26 Sept. 2014. Web. 29 Apr. 2016.

\bibent
“Why Look at Art?” \textit{Khan Academy}, 2012. Web. May 2016.

\bibent
Zoe, Rachel. Personal interview. 16 Apr. 2016.

\bibent
\textit{2015-2016 Undergraduate Business School Handbook}. Texas A\&M University Department of Management: College Station, 2015. Print.

\end{flushleft}
\end{workscited} 